HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-11 draft/ms_v1.tex
CModel: basic statistics

    \cmodel{} algorithm is the primary photometric method for galaxies in
    \hscpipe{} that can be seen as an improved version of the SDSS \cmodel{}
    photometry.
    For more details, please see Section 4.9.8 of Bosch\etal (in prep.).
    Basically, \cmodel{} tries to fit each object using a combination of de Vaucouleur
    and exponential profiles that are approximated by multiple Gaussian profiles.
    Despite the limitation of the \cmodel{} method (e.g. sensitive to background
    subtraction and deblender failure), it can deliver robust PSF-corrected fluxes and
    colors for galaxies.

        \item \plan{${\sim}2$--$3$\% of the injected synthetic galaxies are
            ambiguously blended with real objects.}

        \item \plan{Excluding the ambiguously blended ones, ${\sim}4$--$8$\% of the
            remaining synthetic galaxies do not have any match.
            The unmatched galaxies are systematically fainter than the matched ones.
            And the fraction of unmatched synthetic galaxies is also slightly higher
            in the bad seeing \tract{} than the one with good seeing.
            Similarly, $g$- and $i$-band have higher fraction of unmatched objects.
            }

       \item \plan{From the rest of the matched galaxies, we only keep the primary
           detections (\texttt{detect.is-primary=True}) and the ones with clean
           photometry (see Appendix \ref{app:qc} for details).
           For each \tract{}, there are ${\sim}30000$ galaxies left.}

       \item \plan{A tiny fraction of synthetic galaxies is misclassified as
           point sources by \hscpipe{}.
           And the fraction of misclassifications seems to increase with seeing
           (${\sim}1$\% in good seeing \tract{}; ${\sim}4$\% in bad seeing \tract{}).
           We will further discuss in Section \ref{ssec:sg}.}

       \item \plan{We also use $b>0.05$ to define samples of highly blended galaxies.
           Since synthetic galaxies are more extended, their distribution of $b$
           skew more toward the higher value.
           About ${\sim}7$--$9$\% of galaxies are highly blended by this standard.
           The $g$-band has significantly higher fraction of highly blended objects.}

>>>>

    \cmodel{} algorithm is the primary photometric method for galaxies in
    \hscpipe{} that can be seen as an improved version of the SDSS \cmodel{}
    photometry.
    For more details, please see Section 4.9.8 of Bosch\etal (in prep.).
    In short, \cmodel{} tries to fit each object using a combination of de Vaucouleur
    and exponential profiles that are approximated by multiple Gaussian profiles.
    Despite the limitation of the \cmodel{} method (e.g. sensitive to background
    subtraction and deblender failure), it can deliver robust PSF-corrected fluxes and
    colors for galaxies.

    In our tests, we randomly inject ${\sim}40000$ synthetic galaxies into each 
    \tract{}, and select samples for photometric comparisons in a similar way to the
    stars. 
    First, ${\sim}2$--$3$\% of the synthetic galaxies are ambiguously blended with 
    real objects, and are hence removed from the sample. 
    Among the rest of the sample, ${\sim}2$--$7$\% do not have any match in the 
    \synpipe{} results in different \tracts{} and filters. 
    The fraction of unmatched objects is slightly higher for the $g$- and $y$-band. 
    For the same filter, the fraction is always higher for the bad seeing \tract{}.
    The magnitudes of the unmatched galaxies are systematically fainter than the 
    matched ones. 
    In $i$-band, the median input magnitudes for matched and unmatched galaxies are 
    $24.0$ mag and $24.6$ mag.

    After selecting the matched synthetic galaxies with primary detection and 
    clean photometry (see Appendix \ref{app:qc} for details), we have ${\sim}30000$
    galaxies in each \tract{} for comparison.  
    Among these objects, only $<1$\% is misclassified as point sources by \hscpipe{}
    in the good seeing \tract{}.  
    However, for the bad seeing one, the fraction increases to $4$\%.  
    The median input magnitude for these misclassified sources is ${\sim}24.9$ mag 
    in $i$-band, significantly fainter than the median of others.  
    We will further discuss this in Section \ref{ssec:sg}.

    We also use $b>0.1$ to define samples of highly blended galaxies.
    Due to the extended nature, the distributions of $b$ for synthetic galaxies are 
    very different from stars, and skew toward higher values (especially for the 
    bad-seeing \tract{}). 
    About ${\sim}7$--$9$\% of synthetic galaxies are highly blended by this standard.
    The fraction is only slightly higher in the bad-seeing \tract{}, and the 
    $g$-band has the highest fraction of highly blended galaxies. 
    We highlight the highly blended ones in comparisons, and there are more relevant 
    discussions in Section \ref{ssec:blendedness}.

    Although these galaxies span in very wide large ranges of magnitude and 
    structural parameters, the majority of them are faint 
    ($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec). 
    The photometric quality of these galaxies is very challenging, and also crucial
    to several key scientific goals of the HSC survey. 
    At the same time, these samples are unable to provide enough amounts of 
    bright or large galaxies to test. 
    We will supplement results for these galaxies using better samples for them 
    in the future.
